Converging High-Throughput and High-Performance Computing Paradigms: \\ A Case Study of Using Abstractions to Bridge the Divide

### 2017-03-12 overall.tex
Addressing/answering comments V-A

We evaluate the efficiency, scalability and reliability of the PanDA Brokers
along two dimensions: (i) the amount of backfill availability utilized by the
PanDA Brokers; and (ii) the amount of job walltime spent performing detector
simulations. \jhanote{it is difficult to parse what (ii)?}. We based these
evaluations on measuring the number of cores utilized by ATLAS on Titan, the
overall backfill availability, the number of detector simulations performed on
all the resources available to ATLAS and on Titan, and the failure rate of
these simulations. All the measurements were performed between January 2016
and February 2017.

@@

Figure~\ref{fig:backfill-utilization} shows backfill utilization from
January 2016 to February 2017. \jhanote{Neither figure show efficiency. Both show
utilization.} Efficiency is defined as the fraction of Titan’s
cores available via backfill that was utilized by the PanDA Brokers. \jhanote{I would plot the efficiency on the Y2 axis for both.} The brokers
reached 18\% average efficiency \jhanote{this sentence is a bit difficult to parse. Is the 18\% overall efficiency?} with a minimum 8.9\% efficiency on April 2016
and a maximum 33.5\% efficiency on February 2017. The number of total backfill
cores available was 38.1M in April 2016, and 33.1M in February 2017. This shows
that the measured difference in efficiency did not depend on a comparable
difference in total backfill availability.

\begin{figure}[htp]
\includegraphics[clip,width=\columnwidth]{figures/backfill_consumption.png}
\caption{Caption. \jhanote{I would suggest similar style of X-axis as previous figure. Dificult to parse which is April if we are going to call out a specific month. Also consistenty in style is generally good to keep cognitive burden low.}}
\label{fig:backfill-utilization}
\end{figure}

>>>>

We evaluate the efficiency, scalability and reliability of the PanDA Brokers
along two dimensions: (i) the amount of backfill availability utilized by the
PanDA Brokers; and (ii) the amount of % job walltime
runtime spent performing detector simulations. \jhanote{it is difficult to parse
what (ii)?}\mtnote{Better?} We based these evaluations on measuring the number
of cores utilized by ATLAS on Titan, the overall backfill availability, the
number of detector simulations performed on all the resources available to ATLAS
and on Titan, and the failure rate of these simulations. All the measurements
were performed between January 2016 and February 2017.

@@

Figure~\ref{fig:backfill-utilization} shows backfill utilization from January
2016 to February 2017. \jhanote{Neither figure show efficiency. Both show
utilization.} Efficiency is defined as the fraction of Titan’s cores available
via backfill that was utilized by the PanDA Brokers. \jhanote{I would plot the
efficiency on the Y2 axis for both.} The brokers reached 18\% average efficiency
\jhanote{this sentence is a bit difficult to parse. Is the 18\% overall
efficiency?}\mtnote{average across all months considered. Should I call it
``overall''?} with a minimum 8.9\% efficiency on April 2016 and a maximum 33.5\%
efficiency on February 2017. The number of total backfill cores available was
38.1M in April 2016, and 33.1M in February 2017. This shows that the measured
difference in efficiency did not depend on a comparable difference in total
backfill availability.

\begin{figure}[htp]
\includegraphics[clip,width=\columnwidth]{figures/backfill_consumption.png}
\caption{Caption. \jhanote{I would suggest similar style of X-axis as previous figure. Difficult to parse which is April if we are going to call out a specific month. Also consistency in style is generally good to keep cognitive burden low.}}
\label{fig:backfill-utilization}
\end{figure}
